Strings functions analysis

### 2022-08-29 article.tex
functions descriptions added in table
amount of functions added

    \textbf{Java}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.

    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, \\ each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.

    \textbf{Python}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.

    \textbf{C++}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.

    \textbf{JavaScript}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.

    \textbf{Go}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.

    \textbf{C\#}:

    Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.

    \textbf{Swift}:

    \textbf{PHP}: addcslashes, addslashes, bin2hex, chop, chr, chunk\_split, convert\_cyr\_string, convert\_uudecode, convert\_uuencode, count\_chars, crc32, crypt, echo, explode, fprint, get\_html\_translation\_table, hebrev, hebrevc, hex2bin, html\_entity\_decode, htmlentities, htmlspecialchars\_decode, htmlspecialchars, implode, join, lcfirst, levenshtein, localeconv, ltrim, md5, md5\_file, metaphone, money\_format, nl\_langinfo, nl2br, number\_format, ord, parse\_str, print, printf, quoted\_printable\_decode, quoted\_printable\_encode, quotemeta, rtrim, setlocale, sha1, sha1\_file, similar\_text, soundex, sprintf, sscanf, str\_getcsv, str\_ireplace, str\_pad, str\_repeat, str\_replace, str\_rot13, str\_shuffle, str\_split, str\_word\_count, strcasecmp, strchr, strcmp, strcoll, strcspn, strip\_tags, stripcslashes, stripslashes, stripos, stristr, strlen, strnatcasecmp, strnatcmp, strncasecmp, strncmp, strpbrk, strpos, strrchr, strrev, strripos, strrpos, strspn, strstr, strtok, strtolower, strtoupper, strtr, substr, substr\_compare, substr\_count, substr\_replace, trim, ucfirst, ucwords, vfprintf, vprintf, vsprintf, wordwrap.

    \textbf{Rust}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.

@@

            capitalize &  &  &  &  &  & &  &  & 1 & 1 \\

@@

            compare &  &  &  &  &  & &  &  & n & n \\

            compare-ignore-case &  &  &  &  &  & &  &  &  & \\

            concatenate &  &  &  &  &  & &  &  & n & n \\

            containts &  &  &  &  &  & &  &  & n & n \\

            count &  &  &  &  &  & &  &  &  & \\

            ends-with &  &  &  &  &  & &  &  & n & n \\

            equals &  &  &  &  &  & &  &  & n & n \\

            find-first &  &  &  &  &  & &  &  & n & n \\

            find-last &  &  &  &  &  & &  &  & n & n \\

            format &  &  &  &  &  & &  &  & n & n \\

            hash &  &  &  &  &  & &  &  & n & n \\

            insert &  &  &  &  &  & &  &  & n & n \\

            is-alphabetic &  &  &  &  &  & &  &  & n & n \\

            is-empty &  &  &  &  &  & &  &  & 1 & 1 \\

            is-hexadecimal &  &  &  &  &  & &  &  & n & n \\

            is-int &  &  &  &  &  & &  &  & n & n \\

            is-lowercase &  &  &  &  &  & &  &  & n & n \\

            is-uppercase &  &  &  &  &  & &  &  & n & n \\

            is-whitespace &  &  &  &  &  & &  &  & n & n \\

            join &  &  &  &  &  & &  &  & n & n \\

            length &  &  &  &  &  & &  &  & 1 & 1 \\

            matches-regexp &  &  &  &  &  & &  &  & n & n \\

            partition &  &  &  &  &  & &  &  & n & n \\

            repeat &  &  &  &  &  & &  &  & n & n \\

            replace-all &  &  &  &  &  & &  &  & n & n \\

            replace-first &  &  &  &  &  &  &  &  &  & \\

            split &  &  &  &  &  & &  &  & n & n \\

            starts-with &  &  &  &  &  & &  &  & n & n \\

            strip &  &  &  &  &  & &  &  & n & n \\

            substring &  &  &  &  &  & &  &  & n & 1 \\

            swap-case &  &  &  &  &  & &  &  & n & n \\

            to-float &  &  &  &  &  & &  &  & n & n \\

            to-int &  &  &  &  &  & &  &  & n & n \\

            to-lowercase &  &  &  &  &  & &  &  & n & n \\

            to-uppercase &  &  &  &  &  & &  &  & n & n \\

            trim-left &  &  &  &  &  & &  &  & n & n \\

            trim-right &  &  &  &  &  & &  &  & n & n \\

            reverse &  &  &  &  &  & &  &  & n & 1 \\

            remove &  &  &  &  &  & &  &  &  & \\

            uncapitalize &  &  &  &  &  & &  &  &  & \\

            as-bytes &  &  &  &  &  & &  &  &  & \\

            chop &  &  &  &  &  & &  &  &  & \\ \hline
        \end{tabular}
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{table*}

>>>>

    \textbf{Java (39)}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.

    \textbf{Ruby (132)}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, \\ each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.

    \textbf{Python (45)}: capitalize, casefold, center, count, encode, endswith, expandtabs, find, format, format\_map, index, isalnum, isalpha, isascii, isdecimal, isdigit, isidentifier, islower, isnumeric, isprintable, isspace, istitle, isupper, join, ljust, lower, lstrip, maketrans, partition, replace, rfind, rindex, rjust, rpartition, rsplit, rstrip, split, splitlines, startswith, strip, swapcase, title, translate, upper, zfill.

    \textbf{C++ (43)}: append, assign, at, back, begin, c\_str, capacity, cbegin, cend, clear, compare, copy, crbegin, crend, data, empty, end, erase, find, find\_first\_not\_of, find\_first\_of, find\_last\_not\_of, find\_last\_of, front, get\_allocator, insert, length, max\_size, operator[], operator+=, operator=, pop\_back, push\_back, rbegin, rend, replace, reserve, resize, rfind, shrink\_to\_fit, size, substr, swap.

    \textbf{JavaScript (29)}: charAt, charCodeAt, codePointAt, concat, constructor, endsWith, fromCharCode, includes, indexOf, lastIndexOf, length, localeCompare, match, prototype, repeat, replace, search, slice, split, startsWith, substr, substring, toLocaleLowerCase, toLocaleUpperCase, toLowerCase, toString, toUpperCase, trim, valueOf.

    \textbf{Go (54)}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.

    \textbf{C\# (21)}: Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.

    \textbf{Swift (48)}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun:, removeSubrange, exponentBitCount:, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.

    \textbf{PHP (98)}: addcslashes, addslashes, bin2hex, chop, chr, chunk\_split, convert\_cyr\_string, convert\_uudecode, convert\_uuencode, count\_chars, crc32, crypt, echo, explode, fprint, get\_html\_translation\_table, hebrev, hebrevc, hex2bin, html\_entity\_decode, htmlentities, htmlspecialchars\_decode, htmlspecialchars, implode, join, lcfirst, levenshtein, localeconv, ltrim, md5, md5\_file, metaphone, money\_format, nl\_langinfo, nl2br, number\_format, ord, parse\_str, print, printf, quoted\_printable\_decode, quoted\_printable\_encode, quotemeta, rtrim, setlocale, sha1, sha1\_file, similar\_text, soundex, sprintf, sscanf, str\_getcsv, str\_ireplace, str\_pad, str\_repeat, str\_replace, str\_rot13, str\_shuffle, str\_split, str\_word\_count, strcasecmp, strchr, strcmp, strcoll, strcspn, strip\_tags, stripcslashes, stripslashes, stripos, stristr, strlen, strnatcasecmp, strnatcmp, strncasecmp, strncmp, strpbrk, strpos, strrchr, strrev, strripos, strrpos, strspn, strstr, strtok, strtolower, strtoupper, strtr, substr, substr\_compare, substr\_count, substr\_replace, trim, ucfirst, ucwords, vfprintf, vprintf, vsprintf, wordwrap.

    \textbf{Rust (35)}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.

@@

            String \textbf{capitalize} &  &  &  &  &  & &  &  & 1 & 1 \\

@@

            Strings \textbf{compare} &  &  &  &  &  & &  &  & n & n \\

            Strings \textbf{compare-ignore-case} &  &  &  &  &  & &  &  &  & \\

            Strings \textbf{concatenate} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{containts} substring &  &  &  &  &  & &  &  & n & n \\

            \textbf{count} of substring in string &  &  &  &  &  & &  &  &  & \\

            Check if \textbf{ends-with} a substring &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{equals} &  &  &  &  &  & &  &  & n & n \\

            \textbf{find-first} substring in string &  &  &  &  &  & &  &  & n & n \\

            \textbf{find-last} substring in string &  &  &  &  &  & &  &  & n & n \\

            \textbf{format} string by regexp &  &  &  &  &  & &  &  & n & n \\

            Get string \textbf{hash} &  &  &  &  &  & &  &  & n & n \\

            \textbf{insert} in string by index &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-alphabetic} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-empty} &  &  &  &  &  & &  &  & 1 & 1 \\

            Check if \textbf{is-hexadecimal} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-int} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-lowercase} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-uppercase} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-whitespace} &  &  &  &  &  & &  &  & n & n \\

            \textbf{join} list of strings &  &  &  &  &  & &  &  & n & n \\

            Get string \textbf{length} &  &  &  &  &  & &  &  & 1 & 1 \\

            Check if string \textbf{matches-regexp} &  &  &  &  &  & &  &  & n & n \\

            Get string \textbf{partition} &  &  &  &  &  & &  &  & n & n \\

            \textbf{repeat} string number of times &  &  &  &  &  & &  &  & n & n \\

            \textbf{replace-all} substrings by other &  &  &  &  &  & &  &  & n & n \\

            \textbf{replace-first} substrings by other &  &  &  &  &  &  &  &  &  & \\

            String \textbf{split} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{starts-with} a substring &  &  &  &  &  & &  &  & n & n \\

            String \textbf{strip} &  &  &  &  &  & &  &  & n & n \\

            Get \textbf{substring} by positions &  &  &  &  &  & &  &  & n & 1 \\

            String \textbf{swap-case} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-float} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-int} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-lowercase} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-uppercase} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{trim-left} &  &  &  &  &  &  &  &  & n & n \\

            String \textbf{trim-righ} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{reverse} &  &  &  &  &  & &  &  & n & 1 \\

            \textbf{remove} substring by positions &  &  &  &  &  & &  &  &  & \\

            String \textbf{uncapitalize} &  &  &  &  &  & &  &  &  & \\

            Get string \textbf{as-bytes} &  &  &  &  &  & &  &  &  & \\

            String \textbf{cut-end} &  &  &  &  &  & &  &  &  & \\ \hline

        \end{tabular}
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{table*}
